Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2024-02-28 writing/paper_mcd19a2.qmd
Added an annual comparison with AQS for MCD19A2.
Put code etc. in the bind mount
so it can be updated without rebuilding the image.

```{r basics}
source.files = "globals libraries util data modeling paper_functions"
for (filename in strsplit(source.files, " ")[[1]])
     source(sprintf("code/%s.R", filename))
suppressPackageStartupMessages(
   {library(patchwork)
    library(gridExtra)
    library(flextable)
  })
the.sat = tools::toTitleCase(Wf$satellite)
IG = knitr::include_graphics
```

@@

We examined `r l = tar_read(satellite.vs.aqs); scales::comma(l$n.aqs.obs)` observations of AQS PM~2.5~ on `r scales::comma(l$n.cell.times)` cell-days. The correlation of the observations with the original satellite values was `r sprintf("%.03f", l$old)`, compared to `r sprintf("%.03f", l$new)` with our corrected values.

>>>>

```{r basics}
source.files = "globals libraries util data modeling paper_functions"
for (filename in strsplit(source.files, " ")[[1]])
     source(sprintf("code/%s.R", filename))
suppressPackageStartupMessages(
   {library(patchwork)
    library(gridExtra)
    library(flextable)
  })
the.sat = tools::toTitleCase(Wf$satellite)
IG = knitr::include_graphics
knitr::opts_knit$set(root.dir = "/data/src/writing")
```

@@

We examined `r l = tar_read(satellite.vs.aqs); scales::comma(l$n.aqs.obs)` observations of AQS PM~2.5~ on `r scales::comma(l$n.cell.times)` cell-days. The correlation of the observations with the original satellite values was `r sprintf("%.03f", l$old)`, compared to `r sprintf("%.03f", l$new)` with our corrected values. In a year-level comparison, against `r l = tar_read(satellite.vs.aqs.yearly); scales::comma(l$n.cell.times)` cell-years of AQS annual means, we found a correlation with the original satellite values of `r sprintf("%.03f", l$old)`, compared to `r sprintf("%.03f", l$new)` with our corrected values.
